---
title: "Design"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Design}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(stocktipr)
```

## Design Patterns

This vignette covers the design patterns used to build the modules in `stocktipr`.

### 1. Function-Based Module Pattern

Each module is a pair of functions, `mod_<name>_ui()` and `mod_<name>_server()`, co-located in a single `R/mod_<name>.R` file. The UI function returns a Shiny tag object; the server function wraps its logic in `shiny::moduleServer()`.

``` r
inputs_r <- mod_inputs_server("inputs")

bslib::page_sidebar(
  sidebar = mod_inputs_ui("inputs"),
  mod_outputs_ui("outputs")
)
```

There is no persistent object between the UI call and the server call — the pairing is a naming convention, not an enforced binding.

### 2. Namespace Creation via `shiny::NS()`

Each function calls `shiny::NS(id)` independently:

``` r
mod_inputs_ui <- function(id) {
  ns <- shiny::NS(id)  # created in the UI function
  shiny::selectizeInput(inputId = ns("tickers"), ...)
}

mod_inputs_server <- function(id) {
  shiny::moduleServer(id, function(input, output, session) {
    input$tickers  # namespaced automatically by moduleServer()
  })
}
```

The same `id` string must be passed to both the UI and server calls in `app_ui()` / `app_server()` for the namespaces to line up — there is no shared object enforcing this, so the discipline is naming-convention only (`mod_inputs_ui("inputs")` pairs with `mod_inputs_server("inputs")`).

### 3. Reactive Dependency Injection via Function Arguments

Downstream modules receive upstream reactives as ordinary function arguments:

``` r
# in app_server
inputs_r <- mod_inputs_server("inputs")
perf_r   <- mod_outputs_server("outputs", inputs_r = inputs_r)
           mod_download_server("download", inputs_r = inputs_r, perf_r = perf_r)
```

Each module's dependencies are visible directly in its function signature, which makes the top-down reactive flow explicit and easy to trace from `app_server()` alone.

### 4. Reactive Composition Inside `moduleServer()`

Inside `mod_outputs_server()`, a chain of local reactives builds up the performance pipeline step by step:

``` r
prices_r <- shiny::eventReactive(inputs_r()$fetch, {
  get_stock_prices(tickers = inp$tickers, from = inp$from, to = inp$to)
})

returns_r <- shiny::reactive({
  get_stock_returns(prices_r())
})

perf_r <- shiny::reactive({
  summarise_performance(returns_r())
})
```

Each reactive depends only on the one before it, so the pipeline can be reasoned about (and tested) one stage at a time.

### 5. Logging with Namespace Isolation

Every `logger::log_*()` call carries an explicit `namespace` string scoped to its module:

``` r
logger::log_info(
  "Fetch button pressed | tickers: [{paste(input$tickers, collapse = ', ')}]",
  namespace = "stocktipr/inputs"
)

# Filter by namespace in development
app_set_log_threshold(logger::DEBUG)                                    # all namespaces
logger::log_threshold(logger::DEBUG, namespace = "stocktipr/outputs")  # one namespace
```

This makes it possible to silence noisy modules while debugging a specific one. See `vignette("implementation")` for the full namespace table and log-level reference.
