---
title: "Module structure"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Module structure}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(collapse = TRUE, comment = "#>", eval = FALSE)
```

`stocktipr` is organized as a collection of Shiny modules, wired together in the `app_server()`. This vignette explains the naming convention, the UI/server split, how data flows between modules, and the role each module plays.

------------------------------------------------------------------------

## Naming convention

Every module follows the same file-and-function layout:

| File | UI function | Server function |
|------------------------|------------------------|------------------------|
| `R/mod_inputs.R` | `mod_inputs_ui(id)` | `mod_inputs_server(id)` |
| `R/mod_outputs.R` | `mod_outputs_ui(id)` | `mod_outputs_server(id, inputs_r)` |
| `R/mod_download.R` | `mod_download_ui(id)` | `mod_download_server(id, inputs_r, perf_r)` |

The two tooltip helpers (`mod_tooltip()` and `mod_hoverinfo()`) are *not* modules in the Shiny sense; they have no server counterpart and no `moduleServer()` call.

They are UI / rendering helpers that happen to share the `mod_` prefix for discoverability.

------------------------------------------------------------------------

## Module wiring

`app_ui()` composes the three UI functions into a `bslib::page_sidebar()` layout. The download module UI is embedded *inside* the inputs sidebar rather than at the top level, so the sidebar contains all user controls in one place.

```{r}
app_ui <- function() {
  bslib::page_sidebar(
    sidebar = mod_inputs_ui("inputs"),   # sidebar: includes mod_download_ui()
    mod_outputs_ui("outputs")            # main panel
  )
}
```

`app_server()` wires the three server functions together. The outputs server returns a reactive (`perf_r`) that the download server consumes (his is the only inter-module dependency).

```{r}
app_server <- function(input, output, session) {
  app_set_log_threshold(logger::INFO)

  inputs_r <- mod_inputs_server("inputs")
  perf_r   <- mod_outputs_server("outputs", inputs_r)
             mod_download_server("download", inputs_r, perf_r)
}
```

The reactive data flow is strictly top-down:

```         
mod_inputs_server()  ──► inputs_r  ──► mod_outputs_server()  ──► perf_r  ──► mod_download_server()
```

No module reaches up into its parent or sideways into a sibling.

------------------------------------------------------------------------

## Inputs: `mod_inputs`

**Files:** `R/mod_inputs.R`\
**Exports:** `mod_inputs_ui()`, `mod_inputs_server()`

### UI function

`mod_inputs_ui(id)` returns a `bslib::sidebar()` containing:

-   `selectizeInput` — multi-select ticker picker (user-creatable entries)
-   `dateRangeInput` — date range (defaults to the past year)
-   `sliderInput` — rolling-volatility window, 5–120 trading days
-   `actionButton` — "Fetch data" trigger
-   `mod_download_ui("download")` — embedded at the bottom

`mod_tooltip()` with `type = "bslib"` is used on the ticker and vol-window labels to attach `bslib` popovers without any server-side code:

```{r}
shiny::selectizeInput(
  inputId = ns("tickers"),
  label   = shiny::tags$span(
    "Tickers",
    mod_tooltip(
      trigger  = bsicons::bs_icon("info-circle"),
      type     = "bslib",
      contents = "Enter one or more stock ticker symbols (e.g. AAPL, MSFT).",
      size     = "0.85rem",
      style    = "color:#6c757d"
    )
  ),
  # ...
)
```

### Server function

`mod_inputs_server(id)` logs the fetch event and validates that at least one ticker is selected, then returns a **reactive list**:

```{r}
list(
  tickers    = character(),  # selected ticker symbols
  from       = Date,         # start of date range
  to         = Date,         # end of date range
  vol_window = integer(),    # rolling-vol window in trading days
  fetch      = integer()     # action-button counter (used as event trigger)
)
```

The `fetch` element is an integer counter incremented each time the button is pressed. Downstream modules use `eventReactive(inputs_r()$fetch, ...)` to re-run only when the user explicitly requests new data.

------------------------------------------------------------------------

## Outputs: `mod_outputs`

**Files:** `R/mod_outputs.R`\
**Exports:** `mod_outputs_ui()`, `mod_outputs_server()`

### UI function

`mod_outputs_ui(id)` returns a `shiny::tagList()` with two pieces:

1.  `shiny::uiOutput(ns("value_boxes"))` — KPI value boxes rendered server-side so the number of boxes matches the number of selected tickers.
2.  `bslib::navset_card_tab()` — five demo tabs, one per tooltip back-end.

| Tab | Back-end | Interaction |
|------------------------|------------------------|------------------------|
| `bslib` | `bslib::popover()` via `mod_tooltip()` | Click info icon |
| `shinyhelper` | `shinyhelper::helper()` via `mod_tooltip()` | Click circled-? |
| `prompter` | `prompter::add_prompt()` via `mod_tooltip()` | Hover over label |
| `shinyalert` | `data-sa-*` attrs + delegated JS via `mod_tooltip()` | Click ticker card |
| reactable | `htmltools` `<span title>` via `mod_hoverinfo()` | Hover over cell |

### Server function

**`mod_outputs_server(id, inputs_r)`** is the computational core of the app. It registers `shinyhelper::observe_helpers()` once per session (required by `shinyhelper`; do not call it separately in `app_server()`), then chains four reactives triggered by `inputs_r()$fetch`:

```{r}
# 1 — fetch adjusted prices
prices_r <- shiny::eventReactive(inputs_r()$fetch, {
  get_stock_prices(
    tickers = inp$tickers,
    from    = inp$from,
    to      = inp$to
  )
})

# 2 — daily log returns
returns_r <- shiny::reactive({
  get_stock_returns(prices_r())
})

# 3 — annualised performance summary
perf_r <- shiny::reactive({
  summarise_performance(returns_r())
})

# 4 — five renderUI / renderReactable outputs that consume perf_r()
```

`perf_r` is returned to `app_server()` so `mod_download_server()` can embed it in the rendered report without re-computing it.

### KPI value boxes

The value boxes are colored by Sharpe ratio threshold:

```{r}
theme <- if (sharpe >= 1) "success" else if (sharpe >= 0) "warning" else "danger"
```

### `reactable` tab and `mod_hoverinfo()`

The `reactable` tab is the only output that uses `mod_hoverinfo()`. Each numeric column in the performance table gets a `colDef` cell renderer that wraps the formatted value in an `htmltools` `<span title="...">`:

```{r}
reactable::colDef(
  name = "Ann. Return (%)",
  html = TRUE,
  cell = function(value, index) {
    mod_hoverinfo(
      type     = "reactable",
      contents = glue::glue(
        "Annualised log return for {df$symbol[index]}: {value}%"
      ),
      display  = glue::glue("{value}%"),
      style    = paste0(
        "color:", if (value >= 0) "#198754" else "#dc3545",
        "; cursor:help"
      )
    )
  }
)
```

------------------------------------------------------------------------

## Downloads: `mod_download`

**Files:** `R/mod_download.R`\
**Exports:** `mod_download_ui()`, `mod_download_server()`

### UI function

`mod_download_ui(id)` returns a `bslib::card()` with:

-   `selectInput` — report format (`"html"` or `"pdf"`)
-   `downloadButton` — triggers the handler

The `card` is embedded at the bottom of the inputs sidebar by `mod_inputs_ui()`:

```{r}
# inside mod_inputs_ui()
bslib::sidebar(
  # ... other inputs ...
  mod_download_ui("download")
)
```

This keeps all user controls in the sidebar while the download server is wired at the top level in `app_server()`.

### Server

`mod_download_server(id, inputs_r, perf_r)` renders `inst/report_template.Rmd` into a temporary directory via `rmarkdown::render()` and serves the output through `shiny::downloadHandler()`.

Below are the parameters passed to the template:

```{r}
params = list(
  tickers    = inp$tickers,
  from       = as.character(inp$from),
  to         = as.character(inp$to),
  vol_window = inp$vol_window,
  perf_data  = perf_r()
)
```

Rendering into an isolated `tempfile()` directory ensures the Shiny session working directory is not affected and simultaneous downloads do not collide.

------------------------------------------------------------------------

## Tooltip helpers

These two functions share the `mod_` prefix but are not Shiny modules.

### `mod_tooltip()`

A UI helper — returns a `shiny.tag` with no server counterpart. Place it anywhere inside a UI tree, including inside `renderUI()`.

```{r}
mod_tooltip(
  trigger     = bsicons::bs_icon("info-circle"),  # clickable/hoverable element
  type        = "bslib",      # "bslib" | "shinyhelper" | "prompter" | "shinyalert"
  contents    = "Help text.",
  size        = NULL,         # CSS font-size for the wrapper span
  style       = NULL,         # inline CSS for the wrapper span
  helper_type = "inline",     # shinyhelper only
  helper_size = "m",          # shinyhelper only
  alert_type  = "info",       # shinyalert only
  ...                         # forwarded to the back-end
)
```

### `mod_hoverinfo()`

A rendering helper — returns an `htmltools` `<span title="...">` for use inside `reactable::colDef(cell = ..., html = TRUE)`.

```{r}
mod_hoverinfo(
  type     = "reactable",    # only supported back-end
  contents = character(0),   # tooltip text; named vector → "Name: value" pairs
  display  = NULL,           # visible cell value
  size     = NULL,           # CSS font-size
  style    = NULL,           # inline CSS
  ...                        # extra HTML attributes on the <span>
)
```

------------------------------------------------------------------------

## Adding a new module

Follow these steps to add a fourth module to the app.

**1.** Create `R/mod_<name>.R` with `mod_<name>_ui()` and `mod_<name>_server()`, both exported with `@export`.

**2.** Add the UI call to `app_ui()`:

```{r}
# app_ui.R
bslib::page_sidebar(
  sidebar = mod_inputs_ui("inputs"),
  mod_outputs_ui("outputs"),
  mod_<name>_ui("<name>")     # add here
)
```

**3.** Wire the server in `app_server()`:

```{r}
# app_server.R
mod_<name>_server("<name>", inputs_r, perf_r)
```

**4.** Run `devtools::document()` to update `NAMESPACE` and regenerate the help page, then `pkgdown::build_site()` to update the reference index.