---
title: "Structure"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Structure}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(stocktipr)
```

## Module Wiring

`stocktipr` is organized as a collection of Shiny modules, wired together in `app_server()`. Every module follows the same file-and-function layout:

| File | UI function | Server function |
|------------------------|------------------------|------------------------|
| `R/mod_inputs.R` | `mod_inputs_ui(id)` | `mod_inputs_server(id)` |
| `R/mod_outputs.R` | `mod_outputs_ui(id)` | `mod_outputs_server(id, inputs_r)` |
| `R/mod_download.R` | `mod_download_ui(id)` | `mod_download_server(id, inputs_r, perf_r)` |

The two tooltip helpers (`mod_tooltip()` and `mod_hoverinfo()`) are *not* modules in the Shiny sense; they have no server counterpart and no `moduleServer()` call. They are UI / rendering helpers that happen to share the `mod_` prefix for discoverability.

`app_ui()` composes the three UI functions into a `bslib::page_sidebar()` layout. The download module UI is embedded *inside* the inputs sidebar rather than at the top level, so the sidebar contains all user controls in one place.

```{r app-ui, eval = FALSE}
app_ui <- function() {
  bslib::page_sidebar(
    sidebar = mod_inputs_ui("inputs"),   # sidebar: includes mod_download_ui()
    mod_outputs_ui("outputs")            # main panel
  )
}
```

`app_server()` wires the three server functions together. The outputs server returns a reactive (`perf_r`) that the download server consumes — the only inter-module dependency:

```{r app-server, eval = FALSE}
app_server <- function(input, output, session) {
  app_set_log_threshold(logger::INFO)

  inputs_r <- mod_inputs_server("inputs")
  perf_r   <- mod_outputs_server("outputs", inputs_r)
             mod_download_server("download", inputs_r, perf_r)
}
```

The reactive data flow is strictly top-down:

```
mod_inputs_server()  ──► inputs_r  ──► mod_outputs_server()  ──► perf_r  ──► mod_download_server()
```

No module reaches up into its parent or sideways into a sibling.

------------------------------------------------------------------------

## File Structure

### R/ Directory (Core Implementation)

#### Module Functions

1.  **`mod_inputs.R`**
    -   **Lines**: 162
    -   **Exports**: `mod_inputs_ui(id)`, `mod_inputs_server(id)`
    -   **Key Features**: ticker picker, date range, rolling-vol slider, fetch button, embedded `mod_download_ui()`; fetch-button observer and reactive inputs list on the server side
2.  **`mod_outputs.R`**
    -   **Lines**: 542
    -   **Exports**: `mod_outputs_ui(id)`, `mod_outputs_server(id, inputs_r)`
    -   **Key Features**:
        -   Five tooltip/hover demo tabs (bslib, shinyhelper, prompter, shinyalert, reactable)
        -   Reactive data pipeline (prices → returns → performance)
        -   KPI value boxes with color-coded Sharpe ratios
3.  **`mod_download.R`**
    -   **Lines**: 161
    -   **Exports**: `mod_download_ui(id)`, `mod_download_server(id, inputs_r, perf_r)`
    -   **Key Features**: HTML/PDF report generation via a parameterised R Markdown template, rendered into an isolated temp directory

#### App-Level Functions

4.  **`app_ui.R`** (`app_ui()`)
    -   **Lines**: 108
    -   **Purpose**: Top-level UI composition
    -   **Pattern**: Calls each module's UI function and composes them into `bslib::page_sidebar()`
    -   **Features**: Custom theme (`stocktipr_theme()`), `stocktipr_head()` CSS injection, delegated event handlers for shinyalert/shinyhelper
5.  **`app_server.R`** (`app_server()`)
    -   **Lines**: 57
    -   **Purpose**: Top-level server orchestration
    -   **Pattern**: Calls each module's server function and wires the reactive dependencies between them
    -   **Features**: Logging threshold setup, shinyhelper initialization, session lifecycle logging
6.  **`launch.R`** (`launch()`)
    -   **Lines**: 28
    -   **Purpose**: Convenience wrapper for launching the Shiny app
    -   **Features**: Installs the reactable theme globally, supports passing custom options to `shiny::shinyApp()`

#### Helper/Utility Functions

7.  **`mod_tooltip.R`** (`mod_tooltip()`)
    -   **Lines**: 205
    -   **Type**: Pure UI helper function (no paired server)
    -   **Purpose**: Unified interface for four tooltip backends — bslib, shinyhelper, prompter, shinyalert
8.  **`mod_hoverinfo.R`** (`mod_hoverinfo()`)
    -   **Lines**: 95
    -   **Type**: Server-side helper for reactable cells
    -   **Purpose**: Wraps content with a `title` attribute for native tooltips
9.  **`with_logging.R`** / **`app_set_log_threshold.R`**
    -   **Lines**: 47 / 42
    -   **Purpose**: Structured logging with namespace-based filtering — see `vignette("implementation")`
10. **`utils_operators.R`**
    -   **Lines**: 15
    -   **Operators**: `%||%` (null-coalescing operator)
11. **Financial data/logic functions**
    -   `get_stock_prices.R`, `get_stock_returns.R`, `summarise_performance.R`, `compute_rolling_vol.R`, `get_ff3_factors.R`, `default_tickers.R`
    -   **Purpose**: Reusable data utilities for fetching prices and computing returns, volatility, and performance summaries
12. **Theme functions**
    -   `setup_theme.R`, `custom_head.R`, `utils_reactable_theme.R`
    -   **Purpose**: Dark Bloomberg-terminal styling — see `vignette("theme")`

### Supporting Files

-   **`DESCRIPTION`** — Package metadata, dependencies
-   **`LICENSE`** / **`LICENSE.md`** — MIT license
-   **`README.md`** — Package overview
-   **`inst/report_template.Rmd`** — Parameterised R Markdown template used by `mod_download_server()`
-   **`.Rbuildignore`** / **`.gitignore`** — Build and version-control exclusions

------------------------------------------------------------------------

## Adding a New Module

Follow these steps to add a fourth module to the app.

**1.** Create `R/mod_<name>.R` with `mod_<name>_ui()` and `mod_<name>_server()`, both exported with `@export`.

**2.** Add the UI call to `app_ui()`:

```{r add-module-ui, eval = FALSE}
# app_ui.R
bslib::page_sidebar(
  sidebar = mod_inputs_ui("inputs"),
  mod_outputs_ui("outputs"),
  mod_<name>_ui("<name>")     # add here
)
```

**3.** Wire the server in `app_server()`:

```{r add-module-server, eval = FALSE}
# app_server.R
mod_<name>_server("<name>", inputs_r, perf_r)
```

**4.** Run `devtools::document()` to update `NAMESPACE` and regenerate the help page, then `pkgdown::build_site()` to update the reference index.
