---
title: "Theme"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Theme}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(stocktipr)
```

## Overview

`stocktipr` ships a dark, Bloomberg-terminal aesthetic: a near-black background, cyan primary accent, amber / green / red data colors, and IBM Plex Mono typography throughout. The look is produced by three cooperating pieces.

### Color palette

Every surface draws from one shared set of CSS custom properties, defined in `stocktipr_head()`:

| Token           | Hex       | Role                        |
|-----------------|-----------|-----------------------------|
| `--bbg-bg`      | `#0b0e13` | App background (near-black) |
| `--bbg-panel`   | `#12161d` | Cards, tables, sidebar      |
| `--bbg-panel-2` | `#1a1f28` | Headers, inputs, hovers     |
| `--bbg-border`  | `#2a313b` | Borders and gridlines       |
| `--bbg-cyan`    | `#00d9ff` | Primary / brand accent      |
| `--bbg-amber`   | `#ff9e1b` | Secondary / amber accent    |
| `--bbg-amber-2` | `#ffbf57` | Hover / bright amber        |
| `--bbg-green`   | `#2ecc71` | Success / up                |
| `--bbg-red`     | `#ff4d4f` | Danger / down               |
| `--bbg-cyan`    | `#4ea1ff` | Info / links                |
| `--bbg-text`    | `#d5dde5` | Body text                   |
| `--bbg-dim`     | `#8b95a1` | Muted labels                |
| `--bbg-white`   | `#f2f5f8` | Headings / values           |

Typography is IBM Plex Mono throughout (headings, body, and code), giving the app a fixed-width terminal feel.

### Helper functions

`stocktipr_theme()`: Exported. Returns a `bslib::bs_theme()` object passed to `theme =` in `bslib::page_sidebar()` inside `app_ui()`. It sets the semantic Bootstrap colors (`primary` cyan, `secondary` amber, `success` green, `warning` amber, `danger` red, `info` bright cyan), the dark `bg` / `fg`, panel and border variables, and IBM Plex Mono as the base, heading, and monospace font.

`stocktipr_head()`: Internal (`@noRd`), called by `app_ui()`. Emits the `<head>` tags: the Google Fonts link for IBM Plex Mono / Sans and the inline `<style>` block that defines the palette tokens above and styles navbar, cards, value boxes, buttons, tabs, tables, alerts, the sidebar, scrollbars, a `.rt-*` reactable fallback, and the third-party widgets that don't inherit `bslib` theme variables automatically — `selectize` (ticker picker), `ionRangeSlider` (rolling-vol window), `bootstrap-datepicker` (date range), popovers, and the `shinyhelper` modal.

`utils_reactable_theme()`: Internal. Returns a `reactable::reactableTheme()` matching the palette (dark panels, amber uppercase headers, mono tabular numerals, amber row highlight, dark search / filter / select inputs). `launch()` installs it globally with `options(reactable.theme = utils_reactable_theme())`, so the reactable demo table inherits it with no per-call theming.

### Sidebar and value boxes

Two spots set colors directly rather than through the shared theme:

-   `mod_inputs_ui()` passes `bg = "#12161d"` / `fg = "#d5dde5"` to `bslib::sidebar()` so the sidebar panel matches `--bbg-panel` / `--bbg-text` instead of bslib's default light sidebar background.
-   `mod_outputs_server()` gives the KPI value boxes a custom `bslib::value_box_theme(bg = "#00d9ff", fg = "#05070a")` (cyan / near-black) for Sharpe ratios `>= 1`, in place of the Bootstrap `"success"` (green) theme, so the strongest performers read as cyan-on-black to match the primary accent. `"warning"` (amber) and `"danger"` (red) are used unchanged for the middle and low Sharpe tiers.

```{r value-box-theme, eval = FALSE}
theme <- if (sharpe >= 1) {
  bslib::value_box_theme(bg = "#00d9ff", fg = "#05070a")
} else if (sharpe >= 0) {
  "warning"
} else {
  "danger"
}
```

### Module call structure

How the theme pieces are wired together, from the entry point down:

```{r ast-theme, comment = "", message = FALSE, echo = FALSE, eval = FALSE}
library(lobstr)
lobstr::ast(
  launch(
    options(reactable.theme = utils_reactable_theme()),
    shinyApp(
      app_ui(
        theme = stocktipr_theme(),
        stocktipr_head()
      ),
      app_server()
    )
  )
)
```

```{verbatim}
█─launch
├─█─options
│ └─reactable.theme = █─utils_reactable_theme
└─█─shinyApp
  ├─█─app_ui
  │ ├─theme = █─stocktipr_theme
  │ └─█─stocktipr_head
  └─█─app_server
```

### Implementation

**Theme files:**

-   `R/setup_theme.R`: `stocktipr_theme()`
-   `R/custom_head.R`: `stocktipr_head()` with inline CSS injection
-   `R/utils_reactable_theme.R`: `utils_reactable_theme()`

Unlike a stand-alone stylesheet, all custom CSS lives in the single `stocktipr_head()` `<style>` block — there is no external `.css` file to keep in sync.

## `pkgdown` site

The documentation site (`_pkgdown.yml`) mirrors the same palette so the reference site and the running app feel like one product:

| `_pkgdown.yml` bslib var                   | Value         | App equivalent |
|---------------------------------|------------------|----------------------|
| `bg`                                       | `#0b0e13`     | `--bbg-bg`     |
| `fg`                                       | `#d5dde5`     | `--bbg-text`   |
| `primary`                                  | `#00d9ff`     | `--bbg-cyan`   |
| `secondary`                                | `#ff9e1b`     | `--bbg-amber`  |
| `success`                                  | `#2ecc71`     | `--bbg-green`  |
| `info`                                     | `#4ea1ff`     | `--bbg-cyan`   |
| `warning`                                  | `#ff9e1b`     | `--bbg-amber`  |
| `danger`                                   | `#ff4d4f`     | `--bbg-red`    |
| `base_font` / `heading_font` / `code_font` | IBM Plex Mono | `--bbg-mono`   |

`template: theme` uses a dark syntax-highlighting theme so code blocks read against the same near-black background as the rest of the site.