---
title: "Tooltip and Hover-Info Explorer"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Tooltip and Hover-Info Explorer}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment  = "#>",
  eval     = FALSE
)
```

**`stocktipr`** is a Shiny application-package for demoing and comparing tooltip and hover-info approaches in R using real financial data from [Tidy Finance](https://www.tidy-finance.org/r/) (`tidyfinance`) and [tidyquant](https://business-science.github.io/tidyquant/).

------------------------------------------------------------------------

## Package structure

Each module lives in a single file containing both its `_ui()` and `_server()` functions. All other exported objects have one file each.

```         
R/
├── app_server.R              # Wires together function-based modules by calling mod_inputs_server("inputs"), mod_outputs_server("outputs", ...), mod_download_server("download", ...) sequentially; passes reactive values between them.
├── app_set_log_threshold.R   # Logging configuration setup (initializes logger threshold)
├── app_ui.R                  # Top-level UI function; calls mod_inputs_ui(), mod_outputs_ui(), mod_download_ui() to compose the page
├── compute_rolling_vol.R     # Computes rolling volatility metric for stock analysis
├── custom_head.R             # Helper function for displaying data in a compact format
├── default_tickers.R         # Exports default ticker symbols as a package constant 
├── get_ff3_factors.R         # Fetches Fama-French 3-factor data from external source
├── get_stock_prices.R        # Fetches historical stock price data from API
├── get_stock_returns.R       # Calculates stock returns from price data. 
├── launch.R                  # App entry point; calls shinyApp(ui, server)
├── mod_download.R            # Function-based download module; pairs mod_download_ui() and mod_download_server(id) in one file.
├── mod_hoverinfo.R           # Helper that wraps hover/tooltip text for reactable table cells
├── mod_inputs.R              # Function-based inputs module; contains mod_inputs_ui(id) and mod_inputs_server(id) returning reactive list.
├── mod_outputs.R             # Function-based outputs module; consumes inputs_r and renders performance metrics.
├── mod_tooltip.R             # Tooltip icon helper component
├── setup_theme.R             # Theme and styling configuration  
├── summarise_performance.R   # Calculates performance summary metrics (returns, Sharpe ratio, etc.)
├── utils_operators.R         # Custom operators (%>%, %||%, etc.)
├── utils_reactable_theme.R   # reactable table theme utilities
└── with_logging.R            # Logging wrapper utility for side-effect tracking
```

------------------------------------------------------------------------

## Launching the app

```{r}
stocktipr::launch()
```

`launch()` calls `shiny::shinyApp(app_ui(), app_server)` and accepts `...` forwarded to `shiny::shinyApp()` (e.g. `options = list(port = 4000)`).

------------------------------------------------------------------------

## App architecture

### Entry points

| File           | Function       | Role                                     |
|----------------|----------------|------------------------------------------|
| `launch.R`     | `launch()`     | Creates and runs the Shiny app           |
| `app_ui.R`     | `app_ui()`     | Top-level `bslib::page_sidebar()` layout |
| `app_server.R` | `app_server()` | Wires all module servers together        |

### Reactive flow

```         
launch()
  └─ shinyApp(app_ui(), app_server)

app_ui()
  ├─ mod_inputs_ui("inputs")       # sidebar: tickers, dates, vol window, fetch
  └─ mod_outputs_ui("outputs")     # main: KPI boxes + 5 demo tabs

app_server()
  ├─ mod_inputs_server("inputs")   → inputs_r  (reactive list)
  ├─ mod_outputs_server("outputs", inputs_r)
  │    ├─ shinyhelper::observe_helpers()   # registered here, per session
  │    └─ returns perf_r  (reactive tibble)
  └─ mod_download_server("download", inputs_r, perf_r)
```

The download module UI (`mod_download_ui("download")`) is embedded at the bottom of the inputs sidebar inside `mod_inputs_ui()`; its server is wired at the top level in `app_server()`.

------------------------------------------------------------------------

## Modules

All modules follow the `mod_<name>_ui()` / `mod_<name>_server()` convention and are co-located in a single `mod_<name>.R` file.

### Inputs — `mod_inputs.R`

**`mod_inputs_ui(id)`** — returns a `bslib::sidebar()` with:

-   `selectizeInput` — ticker picker (multi-select, user-creatable)
-   `dateRangeInput` — date range
-   `sliderInput` — rolling-volatility window (5–120 trading days)
-   `actionButton` — "Fetch data"
-   `mod_download_ui()` embedded at the bottom

**`mod_inputs_server(id)`** — returns a **reactive list**:

```{r}
list(
  tickers    = character(),   # selected ticker symbols
  from       = Sys.Date(),    # start date
  to         = Sys.Date(),    # end date
  vol_window = 30L,           # rolling-vol window in days
  fetch      = integer()      # action button counter
)
```

### Outputs — `mod_outputs.R`

**`mod_outputs_ui(id)`** — returns a `shiny::tagList()` containing:

-   `shiny::uiOutput` — KPI value boxes (one per ticker)
-   `bslib::navset_card_tab()` — five demo tabs (see below)

**`mod_outputs_server(id, inputs_r)`** — triggered by `inputs_r()$fetch`:

1.  Calls `shinyhelper::observe_helpers()` once per session (registered here)
2.  Calls `get_stock_prices()` → `prices_r`
3.  Calls `get_stock_returns(prices_r())` → `returns_r`
4.  Calls `summarise_performance(returns_r())` → `perf_r`
5.  Renders all outputs (value boxes + five tabs)
6.  **Returns** `perf_r` for the download module

### Download — `mod_download.R`

**`mod_download_ui(id)`** — a `bslib::card()` with a format selector and `downloadButton`.

**`mod_download_server(id, inputs_r, perf_r)`** — renders a parameterised `inst/report_template.Rmd` into HTML or PDF and serves it via `shiny::downloadHandler()`.

------------------------------------------------------------------------

## Data utilities

Financial data is fetched and processed through four functions:

| File | Function | Description |
|------------------------|------------------------|------------------------|
| `get_stock_prices.R` | `get_stock_prices(tickers, from, to)` | Daily adjusted prices via `tidyquant::tq_get()` |
| `get_stock_returns.R` | `get_stock_returns(prices)` | Daily log returns: `log(adjusted / lag(adjusted))` |
| `compute_rolling_vol.R` | `compute_rolling_vol(returns, window)` | Rolling annualised volatility via `slider::slide_dbl()` |
| `summarise_performance.R` | `summarise_performance(returns)` | Per-ticker ann. return, ann. vol, Sharpe ratio |
| `get_ff3_factors.R` | `get_ff3_factors(start_date, end_date)` | Fama-French 3-factor data via `tidyfinance` |
| `default_tickers.R` | `default_tickers` | Character vector of default mega-cap tickers |

### Example usage outside Shiny

```{r}
library(stocktipr)

prices  <- get_stock_prices(c("AAPL", "MSFT"), from = "2024-01-01")
returns <- get_stock_returns(prices)
perf    <- summarise_performance(returns)
vol     <- compute_rolling_vol(returns, window = 30L)
```

------------------------------------------------------------------------

## Tooltip helpers

Two helper functions provide a uniform interface for attaching tooltip and hover content across all five back-ends.

### `mod_tooltip()`

The UIhelper (in `mod_tooltip.R`) returns a `shiny.tag` with no server-side counterpart. Place it anywhere inside a UI tree, including inside `renderUI()`.

```{r}
mod_tooltip(
  trigger     = bsicons::bs_icon("info-circle"),  # default
  type        = c("bslib", "shinyhelper", "prompter", "shinyalert"),
  contents    = "",
  size        = NULL,       # CSS font-size for the wrapper span
  style       = NULL,       # extra inline CSS for the wrapper span
  helper_type = "inline",   # "inline" | "markdown"  (shinyhelper only)
  helper_size = "m",        # "s" | "m" | "l"        (shinyhelper only)
  alert_type  = "info",     # "info"|"success"|"warning"|"error" (shinyalert only)
  ...                       # forwarded to the back-end function
)
```

| `type` | Back-end | Interaction | Extra `...` args |
|------------------|------------------|------------------|------------------|
| `"bslib"` | `bslib::popover()` | Click | `title`, `placement` |
| `"shinyhelper"` | `shinyhelper::helper()` | Click | `title`, `colour`, `icon`, `buttonLabel`, `easyClose`, `fade` |
| `"prompter"` | `prompter::add_prompt()` | Hover | `position`, `rounded`, `bounce`, `arrow`, `animate` |
| `"shinyalert"` | `data-sa-*` attrs + delegated JS | Click | `title`, `confirmButtonText` |

#### `bslib` example

```{r}
mod_tooltip(
  type     = "bslib",
  contents = "Annualised log return = mean daily log return \u00d7 252.",
  title    = "Ann. Return"
)
```

#### `shinyhelper` example

-   `shinyhelper`'s own `.on('click', '.shinyhelper-icon')` binding runs once at page load, so it misses icons injected later by `renderUI`.

    -   This document-level delegated handler catches every click regardless of when the icon was inserted, stops the (now-duplicate) built-in handler via `stopImmediatePropagation()`, then sets the same input that `shinyhelper`'s `observe_helpers()` `shiny::observeEvent()` listens on.

-   `{priority: 'event'}` ensures re-firing when the same ticker is clicked twice in a row (identical value would otherwise be dropped).

***In `app_ui.R`:***

```{r}
shiny::tags$script(htmltools::HTML(
  "$(document).on('click', '.shinyhelper-icon', function(e) {",
  "  e.stopImmediatePropagation();",
  "  var d = $(this).data();",
  "  Shiny.setInputValue('shinyhelper_params', {",
  "    size:      d.modalSize,",
  "    type:      d.modalType,",
  "    title:     d.modalTitle,",
  "    content:   d.modalContent,",
  "    label:     d.modalLabel,",
  "    easyClose: d.modalEasyclose,",
  "    fade:      d.modalFade",
  "  }, {priority: 'event'});",
  "});"
))
```

```{r}
mod_tooltip(
  trigger     = shiny::tags$span("Sharpe Ratio"),
  type        = "shinyhelper",
  contents    = c("Sharpe Ratio", "Assumes a zero risk-free rate."),
  helper_type = "inline",
  helper_size = "m",
  title       = "Sharpe Ratio"
)
```

#### `prompter` example

```{r}
mod_tooltip(
  trigger  = shiny::tags$span("Ann. Vol"),
  type     = "prompter",
  contents = "Annualised volatility = SD of daily log returns \u00d7 \u221a252.",
  position = "right"
)
```

#### `shinyalert` example

The `shinyalert` back-end stores content in `data-sa-*` attributes and fires on click via a delegated `jQuery` handler injected once in `app_ui()`.

***In `app_ui.R`:***

```{r}
shiny::tags$script(htmltools::HTML(
  "$(document).on('click', '.sa-trigger', function () {",
  "  var d = $(this).data();",
  "  swal({",
  "    title:             d.saTitle || '',",
  "    text:              d.saText  || '',",
  "    type:              d.saType  || 'info',",
  "    html:              true,",
  "    confirmButtonText: d.saBtn   || 'OK'",
  "  });",
  "});"
)),
```

No `observeEvent()` or server handler is needed:

```{r}
mod_tooltip(
  trigger           = shiny::tags$span(class = "fs-4 fw-bold", "AAPL"),
  type              = "shinyalert",
  contents          = "Ann. Return: 14.2%<br>Ann. Vol: 22.1%<br>Sharpe: 0.64",
  title             = "AAPL \u2013 Performance Summary",
  alert_type        = "info",
  confirmButtonText = "Close"
)
```

------------------------------------------------------------------------

### `mod_hoverinfo()`

A **r**endering helper (in `mod_hoverinfo.R`) formats hover content for back-ends that build tooltips programmatically inside table-cell renderers.

```{r}
mod_hoverinfo(
  type     = "reactable",   # currently the only supported back-end
  contents = character(0),  # tooltip text; named vector → "Name: value" pairs
  display  = NULL,          # visible cell value (child node of the <span>)
  size     = NULL,          # CSS font-size
  style    = NULL,          # inline CSS (e.g. "color:#198754; cursor:help")
  ...                       # extra HTML attributes on the <span>
)
```

Returns an `htmltools` `<span>` with a `title` attribute. Browsers render this as a native tooltip on hover. Use inside `reactable::colDef(cell = ..., html = TRUE)`.

```{r}
reactable::colDef(
  name = "Ann. Return (%)",
  html = TRUE,
  cell = function(value, index) {
    mod_hoverinfo(
      type     = "reactable",
      contents = glue::glue("Annualised log return for {df$symbol[index]}: {value}%"),
      display  = glue::glue("{value}%"),
      style    = paste0(
        "color:", if (value >= 0) "#198754" else "#dc3545",
        "; cursor:help"
      )
    )
  }
)
```

------------------------------------------------------------------------

## Logging utilities

| File | Function | Description |
|------------------------|------------------------|------------------------|
| `app_set_log_threshold.R` | `app_set_log_threshold(level)` | Sets `logger` threshold across all package namespaces |
| `with_logging.R` | `with_logging(expr, context, ns)` | `tryCatch` wrapper that logs warnings and errors |
| `utils_operators.R` | `%||%` | Null-coalescing operator |

`app_set_log_threshold()` is called once in `app_server()` at session start. Pass `logger::DEBUG` during development for verbose output:

```{r}
# In app_server(), or interactively:
app_set_log_threshold(logger::DEBUG)
```

------------------------------------------------------------------------

## Decision guide

| Where does the tooltip appear?  | Use               | `type`          |
|---------------------------------|-------------------|-----------------|
| Input label / icon in sidebar   | `mod_tooltip()`   | `"bslib"`       |
| Metric card with help modal     | `mod_tooltip()`   | `"shinyhelper"` |
| Metric label — CSS hover        | `mod_tooltip()`   | `"prompter"`    |
| Clickable element → modal alert | `mod_tooltip()`   | `"shinyalert"`  |
| reactable table cell            | `mod_hoverinfo()` | `"reactable"`   |